Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-06-10 paper/1_Initial/manuscript.qmd
updated docx and qmd

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Factor structure and correlates"
author:
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: ~
#     deceased: ~
#   disclosures:
#     study-registration: ~
#     data-sharing: ~
#     related-report: ~
#     conflict-of-interest: ~
#     financial-support: ~
#     gratitude: ~
#     authorship-agreements: ~
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles:
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Roles are optional. 
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    # roles:
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
    affiliations:
      - ref: id1 
# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
keywords: []
# If true, tables and figures are mingled with the text instead of listed at the end of the document.
floatsintext: true
# Numbered lines (.pdf and .docx only)
numbered-lines: true
# File with references
bibliography: bibliography.bib
# Suppress title page
suppress-title-page: false
# Masks references that appear in the masked-citations list
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
---

<!-- Interoception definition -->
Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018]. 
While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns pertaining to how interoception is assessed.

<!-- Interoception measure -->
Various measures of interoception have been developed (see **figure 1** [**TODO: add crossref**]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs. questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes vs. measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, accuracy). 
While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].

<!-- self-reports -->
For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019]. 
However, understanding the exact nature of what is being measured with different questionnaires is crucial, as self-reports might not reflect the same processes as other measures, seemingly contributing to an apparent lack of convergence in the field.

@@

<!-- Introducing the IAS -->
A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019]. The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g. *"I can always accurately perceive when I need to urinate"*). 
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., **TODO: add representative examples**).

<!-- IAS structure  -->
The original validation study suggested a two-factor solution structure, the authors decided... **what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p. XX*].
Most follow-up studies, using a confirmatory factor analysis approach (CFA) **(is that correct?)**, report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items. 
For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (**Can you double check that this paper said this**). @lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor. 
Recently, **@blabla** used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**.

<!-- Convergent validity (correlates)  -->
While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@REF], and positive with neuroticism [@ref]. **anything else?**. 
The IAS has also been compared to other interoception scales, yielding a positive correlation with most facets of the MAIA, with the notable exception of **TODO** [@brand2023], and the **TODO** dimension of the Body Perception Questionnaire [BPQ; @campos2021].
<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->

@@

The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets **(Brand, et al., 2023; Campos, et al., 2021; Lin, et al., 2023; Murphy, et al., 2020)** **[REDO REFS]**. While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data. Thus, providing additionally a individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.

@@

**Table 1.** Samples demographics

| Samples                  |          | Sample Size | Mean age | SD      | Range   | Female % | Available at           |
|---------|---------|---------|---------|---------|---------|---------|---------|
| Murphy et al., (2020)    |          |             |          |         |         |          |                        |
|                          | Sample 1 | 451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        |
|                          | Sample 2 | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> |
| Gaggero et al., (2021)   |          | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> |
| Campos et al., (2022)    |          | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> |
| Todd et al., (2022)      |          | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> |
| Arslanova et al., (2022) |          | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> |
| Brand et al., (2022)     |          | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> |
| Brand et al., (2023)     |          |             |          |         |         |          |                        |
|                          | Sample 1 | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        |
|                          | Sample 2 | 1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> |
|                          | Sample 3 | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |
| Lin et al., (2023)       |          |             |          |         |         |          |                        |
|                          | Sample 1 | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        |
|                          | Sample 2 | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> |
| VonMohr et al., (2023)   |          | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> |
| Makowski et al., (2023a) |          | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation\*\*    |
| Makowski et al., (2023b) |          | 251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation\*\*    |

**TODO: add row for Total N, average age etc.**
**TODO: add language also, as well as maybe something like "difference" from the original validation (which could acctually be language, and for our the type of scale / less items)**
**TODO: add links to GH for our studies**

The analysed sample contains 31,317 participants, of which xxx are females.

@@

| Questionnaire              | Number of Dimensions | Assessment                              | Number of Items | Scoring                | Example Item  |
|-----------------|------------|-------------------|-------------|-------------|-------------|
| **Interoceptive Related**  |                      |                                         |                 |                        |               |
| MAIA-2                     | 8                    | Interoception                           | 37              | 6-point Likert scale   |               |
| BPQ                        | 2                    | Body awareness and autonomic reactivity | 49              | 5-point Likert scale   |               |
| TAS-20                     | 3                    | Alexithymia                             | 20              | 5-point Likert scale   |               |
| BVAQ                       | 2                    | Alexithymia                             | 40              | 5-point Likert scale   |               |
| **Mood**                   |                      |                                         |                 |                        |               |
| BDI-II                     | 1                    | Severity of depressive symptoms         | 21              | 0-to-3-point values    |               |
| PHQ-4                      | 2                    | Anxiety and depressive symptoms         | 4               | 5-point Likert scale   |               |
| STAI-T                     | 1                    | Trait anxiety                           | 20              | 4-point Likert scale   |               |
| GAD-2                      | 1                    | General Anxiety                         | 2               | 4-point Likert scale   |               |
| **Personality**            |                      |                                         |                 |                        |               |
| NEO-FFI                    | 1                    | Neuroticism                             | 12              | 5-point Likert scale   |               |
| Mini IPIP6                 | 6                    | Personality                             | 24              | Analogue scales        |               |
| BFI                        | 5                    | Personality                             | 44              | 5-point Likert scale   |               |
| PID-5-SF                   | 5                    | Dysfunctional personality traits        | 25              | 4-point Likert scale   |               |
| **Psychopathology**        |                      |                                         |                 |                        |               |
| SPQ-BRU                    | 4                    | Schizotypy                              | 32              | 5-point Likert scale   |               |
| MSI-BPD                    | 1                    | Borderline personality disorder         | 10              | Analogue scales        |               |
| ASQ - Short                | 5                    | Autistic Traits                         | 28              | 4-point Likert scale   |               |
| **Beliefs and Misbeliefs** |                      |                                         |                 |                        |               |
| GCB                        | 5                    | Conspiracy beliefs                      | 15              | 5-point Likert scale   |               |
| PI-18                      | 1                    | Beliefs about the world                 | 99              | 6-point Likert scale   |               |
| LIE scale                  | 4                    | Lying tendencies                        | 16              | Visual analogue scales |               |

@@

The analysis revealed a negative correlation between alexithymia and scores in the IAS, which is in line with previous research [@herbert2011]. A negative correlation between autism and interoceptive awareness, which has been found in this sample, has also been found in previous research [@dubois2016]. Conspiracy Beliefs and IAS scores were not strongly correlated. However, there was a slight positive correlation. To the best of our knowledge, this interaction has not been investigated before. However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism \[@ruisch2022\]. Lying profile was also not strongly correlated with the IAS. Previous research provides some evidence for a relationshipbetween interoception and lying profile [@makowski2023a], indicating a contrast from the literature to the results at hand. The analysis showed that mood and the IAS scores have a strong negative correlation, which has been investigated in previous studies, finding a correlation between the two variables as well [@solanolópez2018]. The analysis showed that personality is also correlated with interoceptive accuracy scores as retrieved by the IAS. While there are many aspects of personality, put simply, personality and interoception have been found to correlate in previous studies as well [@erle2021]. Our findings show some negative correlations between schizotypy and interoception. Previous research has investigated this relationship and, similarly, found a negative correlation between interoceptive awareness and schizotypy, particularly at the onset of psychosis [@torregrossa2022]. Lastly, World Beliefs and Interoception showed some significant positive correlations. World Beliefs have not been linked with interoception previously. As mentioned, other beliefs, such as political beliefs have been mentioned to interoception, where significant correlations were observed [@ruisch2022a]. Further research is needed to understand this mechanism and validate whether world beliefs, which lay the framework through which we see the world [@clifton2020], is needed.

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Factor structure and correlates"
author:
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles:
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
---

<!-- Interoception definition -->

Interoception is referred to the process of sensing, interpreting and integrating information pertaining to internal organs, such as the heart, the lungs or the gut [@khalsa2018].
While recent research emphasizes a key role of interoception in a variety of processes (e.g., emotion regulation, decision making) and of outcomes (physical and psychological well being), the field remains clouded by concerns pertaining to how interoception is assessed.

<!-- Interoception measure -->

Various measures of interoception have been developed (see **figure 1** \[**TODO: add crossref**\]), forming a combination of "objective" and "subjective" assessments (i.e., physiological tasks such as the heart beat counting or tracking vs. questionnaires and subjective scales involving a metacognitive reflection), "explicit" and "implicit" paradigms (i.e., directing participants' awareness and attention to interoceptive processes vs. measuring interoception unbeknownst to them), various interoceptive modalities (e.g., cardioception, respiroception, gastroception) and theoretical dimensions (e.g., sensitivity, awareness, accuracy).
While there is no consensus as to which particular approach provides the most accurate and "pure" measure of interoception and interoceptive abilities (assuming it is a unidimensional construct), it is instead plausible that each measure has strengths and limitations, and a utility dependent on the context and goal at hand [@jahedi2014].

<!-- self-reports -->

For instance, while the use of self-reports questionnaires might seem at odds with the concept of interoception (appearing at first as a deeply embodied - almost non-cognitive - sensory function), recent redefinitions of interoception, emphasizing the role of high-level and metacognitive elaboration of interoceptive information, has provided the theoretical grounding to support the idea that some facets of interoception (including participants' metacognitive beliefs) can be assessed subjectively, providing useful and interesting measures [@murphy2019].
However, understanding the exact nature of what is being measured with different questionnaires is crucial, as self-reports might not reflect the same processes as other measures, seemingly contributing to an apparent lack of convergence in the field.

**Figure 1**

Different ways in which interoception can be measured.

@@

<!-- Introducing the IAS -->

A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g. *"I can always accurately perceive when I need to urinate"*).
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., ***"I trust my body sensations"***, ***"I can notice an unpleasant body sensation without worrying about it"***).

<!-- IAS structure  -->

<!-- The original validation study suggested a two-factor solution structure, the authors decided...
**what?**, and underline the need for further investigation of the scale's factor structure [@murphy2019, *p. 127*].
Most follow-up studies, using a confirmatory factor analysis approach (CFA) and exploratory structural equation modeling (**all used CFA but Campos also used ESEM**), report unidimensional structures to be the best fit [@lin2023; @campos2021; @brand2023], although with some discussions about specific items. -->
<!-- For instance, @murphy2019 does mention that some items might be measuring direct interoceptive signals such as cardioception, while others, for instance "bruising", might capture phenomena that cannot be perceived through interoceptive signals alone (*yes* p.119). -->
<!-- @lin2023 also highlights their correlation analysis showing five locally dependent pairs in three items with exceptionally high difficulty and low discrimination, and @campos2021 suggests that the "tickle" item is representing a more specific factor. -->
<!-- Recently, @blabla used a new approach, namely Exploratory Graph Analysis (EGA), and found that **TODO**. -->

The original validation study suggested a two-factor solution structure, the authors however underline the need for further investigation of the scale's factor structure, as it provided acceptable but imperfect explanation of the data [@murphy2019; p. 127].
Notably, the only other validation study to report a 2-factor solution was conducted by @koike2023, who performed an exploratory factor analysis assuming 2 factors to align with the findings from the original validation paper.
Other follow-up studies using confirmatory factor analysis (CFA) and exploratory structural modeling [@morin2016] have identified different optimal solutions. Some studies, like @brand2023, reported a 1-factor solution, while @lin2023 and @campos2021 found bifactor solutions to be the best fit. These studies included discussions on specific items. For instance, @murphy2019 notes that some items might measure direct interoceptive signals such as cardioception, while others, like “bruising,” might capture phenomena not perceivable through interoceptive signals alone (yes p.119). @lin2023 also highlights their correlation analysis, showing five locally dependent pairs and three items with exceptionally high difficulty and low discrimination. Additionally, @campos2021 suggests that the “tickle” item represents a more specific factor.
Interestingly, @lin2023 reported that all items of the IAS grouped together using a new approach, Exploratory Graph Analysis (EGA), to assess convergent and discriminant validity, which suggests unidimensionality.
<!-- TO BE COMPLETED -->

<!-- Convergent validity (correlates)  -->

While the assessment of the validity of an interoception scale can be conceived as theoretically challenging, several traits have been used to assess convergent validity for the the IAS, including expected negative associations with alexithymia [@brand2023; @koike2023; @campos2023, @murphy2019], somatic symptoms [@brand2023; @koike2023], depressive symptoms [@brand2023; @koike2023], anxiety [@brand2023], neuroticism [@brand2023].   
<!-- **anything else?**. TO BE COMPLETED -->
The IAS has also been compared to other interoception scales (and interoceptive related scales), yielding a positive correlation with most facets of the MAIA, with the notable exception of *Non distracting* and *Not worrying* subscales [@brand2023], the body awareness dimension of the Body Perception Questionnaire [BPQ-A; @brand2023; @campos2021; @koike2023; @lin2023], the observation and description scales of the Five Facet Mindfulness Questionnaire [@ref, @brand2023], the interoceptive awareness subscale of the Eating Disorder Inventory [@lin2023] and a negative correlation with interoceptive confusion questionnaire [@brand2023], IATS [@lin2023; @murphy2019].
<!-- TO BE COMPLETED -->

<!-- Moreover, the current subjective measures do not correlate well with the objective measures [@murphy2019]. -->

@@

The goal of study 1 is to re-analyse and assess the factor structure of the IAS by taking advantage of the large number of open-access datasets [@brand2023; @campos2021; @lin2023; @murphy2019; @arslanova2022; @todd2022; @gaggero2021; @brand2022; @von2023].
While combining these studies might provide a more robust and generalizable understanding of the IAS' factor structure, it is important to note that the studies differ in their sample sizes, demographics, language, and the way they collected the data.
Thus, providing additionally a individual analysis (i.e., on all samples individually) will help adding nuance to the general picture.

@@

**Table 1**

Samples demographics.
![Figure 1. Different ways in which interoception can be measured.](figures/table1.png){width="580"}

<!-- **Table 1.** Samples demographics -->

<!-- | Samples                  |          | Language of Items|  Sample Size | Mean age | SD      | Range   | Female % | Available at           | -->

<!-- |---------|---------|---------|---------|---------|---------|---------|---------|---------| -->

<!-- | Murphy et al., (2020)    |          |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | English     |451         | 25.8     | 8.4     | 18-69   | 69.4%    |                        | -->

<!-- |                          | Sample 2 | English     | 375         | 35.3     | 16.9    | 18-91   | 70.1%    | <https://osf.io/3m5nh> | -->

<!-- | Gaggero et al., (2021)   |          | English and Italian   | 814         | 24.9     | 5.3     | 18-58   | 60.3%    | <https://osf.io/5x9sg> | -->

<!-- | Campos et al., (2022)    |          | Portuguese  | 515         | 30.7     | 10.5    | 18-72   | 59.6%    | <https://osf.io/j6ef3> | -->

<!-- | Todd et al., (2022)      |          | English     | 802         | 36.58\*  | 12.41\* | 18-92\* | NA       | <https://osf.io/ms354> | -->

<!-- | Arslanova et al., (2022) |          | English     | 96          | 28.78    | 27.5    | 18-73   | 46.8%    | <https://osf.io/mp3cy> | -->

<!-- | Brand et al., (2022)     |          | German      | 619         | 43.9     | 14.5    | 18-78   | 78.7%    | <https://osf.io/xwz6g> | -->

<!-- | Brand et al., (2023)     |          |             |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | German      | 522         | 23.4     | 6.7     | 18-79   | 79.5%    |                        | -->

<!-- |                          | Sample 2 | German      |1993        | 32.0     | 12.6    | 16-81   | 77.7%    | <https://osf.io/3f2h6> | -->

<!-- |                          | Sample 3 | German      | 802         | 27.3     | 9.3     | 18-72   | 68.9%    |                        |instaiin -->

<!-- | Lin et al., (2023)       |          |             |             |          |         |         |          |                        | -->

<!-- |                          | Sample 1 | Chinese     | 1166        | 32.5     | 8.4     | 16-60   | 57.0%    |                        | -->

<!-- |                          | Sample 2 | Chinese     | 500         | 37.4     | 7.4     | 20-60   | 56.2%    | <https://osf.io/3eztd> | -->

<!-- | VonMohr et al., (2023)   |          | English     | 21843       | 56.5     | 14.4    | 18-93   | 73.2%    | <https://osf.io/7p9u5> | -->

<!-- | Makowski et al., (2023a) |          | English     | 485         | 30.1     | 10.1    | 18-73   | 50.3%    | In preparation \*\*    | -->

<!-- | Makowski et al., (2023b) |          | English     |251         | 37.5     | 13.2    | 17-76   | 53.0%    | In preparation \*\*    | -->

<!-- | Total                    |          |             |31317       | 49.5     | 13.2    | 17 - 93 | 71.5%    | | -->

**Note**.
\* Numbers were sourced from the original paper rather than independently calculated.
\*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>

<!-- **TODO: add row for Total N, average age etc.** -->

**TODO: add language also, as well as maybe something like "difference" from the original validation (which could actually be language, and for our the type of scale / less items)** <!-- **TODO: add links to GH for our studies** -->

The analysed sample contains 31,317 participants, of which 71.5% are females.

@@

| Questionnaire              | Number of Dimensions | Assessment                              | Number of Items | Scoring                | Example Item |
|------------|------------|------------|------------|------------|------------|
| **Interoceptive Related**  |                      |                                         |                 |                        |              |
| MAIA-2                     | 8                    | Interoception                           | 37              | 6-point Likert scale   |              |
| BPQ                        | 2                    | Body awareness and autonomic reactivity | 49              | 5-point Likert scale   |              |
| TAS-20                     | 3                    | Alexithymia                             | 20              | 5-point Likert scale   |              |
| BVAQ                       | 2                    | Alexithymia                             | 40              | 5-point Likert scale   |              |
| **Mood**                   |                      |                                         |                 |                        |              |
| BDI-II                     | 1                    | Severity of depressive symptoms         | 21              | 0-to-3-point values    |              |
| PHQ-4                      | 2                    | Anxiety and depressive symptoms         | 4               | 5-point Likert scale   |              |
| STAI-T                     | 1                    | Trait anxiety                           | 20              | 4-point Likert scale   |              |
| GAD-2                      | 1                    | General Anxiety                         | 2               | 4-point Likert scale   |              |
| **Personality**            |                      |                                         |                 |                        |              |
| NEO-FFI                    | 1                    | Neuroticism                             | 12              | 5-point Likert scale   |              |
| Mini IPIP6                 | 6                    | Personality                             | 24              | Analogue scales        |              |
| BFI                        | 5                    | Personality                             | 44              | 5-point Likert scale   |              |
| PID-5-SF                   | 5                    | Dysfunctional personality traits        | 25              | 4-point Likert scale   |              |
| **Psychopathology**        |                      |                                         |                 |                        |              |
| SPQ-BRU                    | 4                    | Schizotypy                              | 32              | 5-point Likert scale   |              |
| MSI-BPD                    | 1                    | Borderline personality disorder         | 10              | Analogue scales        |              |
| ASQ - Short                | 5                    | Autistic Traits                         | 28              | 4-point Likert scale   |              |
| **Beliefs and Misbeliefs** |                      |                                         |                 |                        |              |
| GCB                        | 5                    | Conspiracy beliefs                      | 15              | 5-point Likert scale   |              |
| PI-18                      | 1                    | Beliefs about the world                 | 99              | 6-point Likert scale   |              |
| LIE scale                  | 4                    | Lying tendencies                        | 16              | Visual analogue scales |              |

@@

The analysis revealed a negative correlation between alexithymia and scores in the IAS, which is in line with previous research [@herbert2011].
A negative correlation between autism and interoceptive awareness, which has been found in this sample, has also been found in previous research [@dubois2016].
Conspiracy Beliefs and IAS scores were not strongly correlated.
However, there was a slight positive correlation.
To the best of our knowledge, this interaction has not been investigated before.
However, research shows correlations between (political) beliefs and interoception, which could underlie the same mechanism [@ruisch2022].
Lying profile was also not strongly correlated with the IAS.
Previous research provides some evidence for a relationshipbetween interoception and lying profile [@makowski2023a], indicating a contrast from the literature to the results at hand.
The analysis showed that mood and the IAS scores have a strong negative correlation, which has been investigated in previous studies, finding a correlation between the two variables as well [@solanolópez2018].
The analysis showed that personality is also correlated with interoceptive accuracy scores as retrieved by the IAS.
While there are many aspects of personality, put simply, personality and interoception have been found to correlate in previous studies as well [@erle2021].
Our findings show some negative correlations between schizotypy and interoception.
Previous research has investigated this relationship and, similarly, found a negative correlation between interoceptive awareness and schizotypy, particularly at the onset of psychosis [@torregrossa2022].
Lastly, World Beliefs and Interoception showed some significant positive correlations.
World Beliefs have not been linked with interoception previously.
As mentioned, other beliefs, such as political beliefs have been mentioned to interoception, where significant correlations were observed [@ruisch2022a].
Further research is needed to understand this mechanism and validate whether world beliefs, which lay the framework through which we see the world [@clifton2020], is needed.
